### 2020-08-17 abstract.tex
fix typos
newver

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from further away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model. To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR. We implement \textsf{SPPeek} in Android. The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses. And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

>>>>

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) techniques, a malicious attacker can peek from further away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model. To underline this concern, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR. We implement \textsf{SRPeek} in Android. The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses. And it outperforms the state-of-the-art and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

### 2020-08-17 conclusion.tex
newver

\section{Conclusion}
\label{sec-conclusion}
In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency. We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection. It is our wish that this work can stir discussion in the field of screen privacy protection and propagate defense mechanisms across critical mobile apps.

>>>>

\section{Conclusion}
\label{sec-conclusion}
In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphones, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency. We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection. It is our wish that this work can stir discussion in the field of screen privacy protection and propagate defense mechanisms across critical mobile apps.

### 2020-08-17 design.tex
newver

\subsection{Design Principle}
To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-system}.
%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network. The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
    \item \textbf{Inconsistency problem, model Complexity and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters. This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames. Furthermore, this allows variations in the number of input images.
    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, instead of using Mean Square Error(MSE) as the loss function, we put a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
  \end{itemize}

\subsection{Network Design}
The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output. The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer. As mentioned before, in each layer images are processed separately, with the merging layers as a revenue for communication, so that the output of each layer is correspondent to the input.  We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer. Till now the model is not different from traditional SR models:
\begin{equation}\label{eq:1}
    \begin{split}
x_i^{(l)} = H_l(x_i^{(l-1)}), i=1,2,...N
\end{split}
\end{equation}

@@

where (p,q) represent the pixel at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator. We use T=5 and k=-1,-0.5,0,0.5,1 in our model, giving consideration to both consensuses (k=0,averaging) and prominent features(k=1, 'soft'max and k=-1, 'soft'min). these $T\times R$ channels $b_{tr}^{(l)}$ is the output of this merging layer $Merge_l$.

>>>>

\subsection{Design Principle}
To solve the challenges and outperform the state-of-the-art for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-system}.
%\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Layered architecture and frequent introduction of input.} In our architecture all input images are processed simultaneously and separately, with the information from other images for reference, throughout the network. The initial input images are introduced into the dataflow at each layer, from beginning to end, forming a model with uneven depth, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
    \item \textbf{Merging layers to adapt multiple frames.} A merging process inside each layer functions as the revenue of communication across images integrates information from all the images into one, the result of which is then stacked with each image for the next convolution. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
    \item \textbf{Inconsistency problem, model complexity, and adaption for variable input.} To counter the lack of consistency between frames, all the convolutional layers throughout the network are performed individually for each image with the same set of parameters. This not only reduces parameter count and calculation power, but also avoids reliance on consistency between neighboring frames. Furthermore, this allows variations in the number of input images.
    \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of deviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, instead of using Mean Square Error(MSE) as the loss function, we put a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighboring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
  \end{itemize}

\subsection{Network Design}
The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output. The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer. As mentioned before, in each layer images are processed separately, with the merging layers as revenue for communication, so that the output of each layer is correspondent to the input.  We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer. Till now the model is not different from traditional SR models:
\begin{equation}\label{eq:1}
    \begin{split}
x_i^{(l)} = H_l(x_i^{(l-1)}), i=1,2,...N
\end{split}
\end{equation}

@@

where (p,q) represents the pixel at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator. We use T=5 and k=-1,-0.5,0,0.5,1 in our model, giving consideration to both consensuses (k=0,averaging) and prominent features(k=1, 'soft'max and k=-1, 'soft'min). these $T\times R$ channels $b_{tr}^{(l)}$ is the output of this merging layer $Merge_l$.

### 2020-08-17 evaluation.tex
newver

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possess up to 5x optical zooming ability which we will utilize fully in our experiments.

@@

In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio(PSNR) to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy. The traditional lens group is trained and tested at 1-2 meters distance, while the optical lens, 5-7.5 meters, where less than 5\% of the characters can be read with the naked eye. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

@@

\subsection{Performance In Random Environments}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments. The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}. We can observe that the model performs best in daytime and at closer distances. For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens. From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical lens. This verifies the efficiency of our model for environment adaption.

@@

\subsection{Performance with fewer available images}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene. This design is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry, where only the last character of the password is visible. We evaluated the impact of fewer available images to the performance of the SR model. The results are shown in fig.~\ref{fig:number_adapting}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

In the tradition lens group the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is available to rule out all possibilities of the displayed characters. The optical lens group displayed a steady decent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
\begin{figure*}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption{Performance (a)(b). with fewer available images and (c)(d). for the adapting ability via traditional lens and optical lens.}
    \label{fig:number_adapting}
\end{figure*}

@@

We observed that variations in light and angle parameter in training data is crucial to a robust model. In the tradition lens group, the variations within 1 and 2 meters may have a smaller impact to the size of the characters
 so that features extracted at one distance might still exist at another.
 However, tilts and angles cause rotations and deformations and severely disturb the feature extraction process. The optical lens group yields similar results except at variations in distance. At a range of 6 meters, increases in distance leads to greater complexity of image blurriness, leading to more complex feature extraction and a more fragile model.
% \begin{figure}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
%     \hfill
%     \caption{Performance for the adapting ability using traditional lens and optical lens.}
%     \label{fig:adapting}
% \end{figure}

\subsection{Comparison with other architectures}
We train and test other widely used networks with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR & 13.32db & 7.69db & 8.403db\\ 
    OCR Accuracy & 100\% & 10\% & 23\%\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

The results show that Human can read 95\%, 85\% and 70\% contents in home, transport and theater while the OCR accuracy is 100\%, 10\% and 23\%. That verifies human can obtain the most parts of information from the peeking in various environments. In transport, the vibration of smartphone and the darker environment can fool the OCR model for content recognition in comparison with human recognition so that leads lower accuracy in transport and theater.

@@

\subsection{Influence of hand tremors}
We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort (Handheld camera). We process these images and let them read the results. We compare this performance to the data collected on stationary phones to evaluate the influence of hand tremors.
We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions (Handheld target). The user may freely interact with the phone when reading. We capture images of the phone at the same time to see how our system deal with a moving target screen. The results are shown in Table~\ref{table-tremor}.

@@

\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters(typing at 2 characters per second). We use accuracy per character as evaluation metric. In the PIN and password tasks, fewer photos will be available, but deciphering English characters is also easier than Chinese characters, and we use specifically trained models(with same structure and different training data). The results are shown in Table~\ref{table-task}.

>>>>

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We perform the following experiments with two commercial off-the-shelf(COTS) smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possesses up to 5$\times$ optical zooming ability which we will utilize fully in our experiments. The Peak Signal to Noise Ratio(PSNR) metric and Optical Character Recognition (OCR) services are used to evaluate the accuracy of our system.

@@

In these experiments, we train and test the model with the images captured with exactly the same environment parameters. The results are shown in Fig.~\ref{fig-control-1} and ~\ref{fig-control-2}. The traditional lens group is trained and tested at 1-2 meters distance, while the optical lens, 5-7.5 meters, where less than 5\% of the characters can be read with the naked eye. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

@@

\subsection{Performance In Random Environments}
We train the model with data captured with varying environmental parameters, and test its ability at a new environment setting. The results are shown in Figure~\ref{fig-random-1} and ~\ref{fig-random-2}. The model can achieve an OCR accuracy above 85\% at 1.8m with traditional lens, and above 90\% at 6m with optical lens. This verifies the efficiency of our model for environment adaption.

@@

\subsection{Performance with fewer available images}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, which is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry. The previous experiments are all conducted with the ideal 20 frames per burst, but in the case study at Sec.~\ref{case-study} and real-life scenarios the attacker only gets to photograph when the screen display remains constant, so there might be fewer images available. We evaluated the impact of fewer available images to the performance of the SR model. The results are shown in fig.~\ref{fig:number_adapting}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

In the traditional lens group, the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is available to rule out all possibilities of the displayed characters. The optical lens group displayed a steady descent of accuracy when fewer images are available, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.
\begin{figure*}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption{Performance (a)(b). with fewer available images and (c)(d). for the adapting ability via traditional lens and optical lens.}
    \label{fig:number_adapting}
\end{figure*}

@@

We observed that variations in light and angle parameter in training data is crucial to a robust model. In the traditional lens group, the variations within 1 and 2 meters may have a smaller impact on the size of the characters
 so that features extracted at one distance might still exist at another.
 However, tilts and angles cause rotations and deformations and severely disturb the feature extraction process. The optical lens group yields similar results except at variations in distance. At a range of 6 meters, increases in distance lead to greater complexity of image blurriness, leading to more complex feature extraction and a more fragile model.
% \begin{figure}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
%     \hfill
%     \caption{Performance for the adapting ability using traditional lens and optical lens.}
%     \label{fig:adapting}
% \end{figure}

\subsection{Comparison with other architectures}
We train and test other widely used networks with the same sets of data and evaluate their results. We chose SRCNN~\cite{dong2015image}, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR~\cite{kappeler2016video}). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR & 13.32db & 7.69db & 8.403db\\ 
    OCR Accuracy & 100\% & 10\% & 23\%\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

The results show that humans can read 95\%, 85\% and 70\% contents in home, transport, and theater while the OCR accuracy is 100\%, 10\% and 23\%. That verifies that humans can obtain the most parts of information from the peeking in various environments. In transport, the vibration of smartphone and the darker environment can fool the OCR model for content recognition in comparison with human recognition so that leads to lower accuracy in transport and theater.

@@

\subsection{Influence of hand tremors}
We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort (Handheld camera). We process these images and let them read the results. We compare this performance to the data collected on stationary phones to evaluate the influence of hand tremors.
We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions (Handheld target). The user may freely interact with the phone when reading. We capture images of the phone at the same time to see how our system deals with a moving target screen. The results are shown in Table~\ref{table-tremor}.

@@

\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters(typing at 2 characters per second). We use accuracy per character as the evaluation metric. In the PIN and password tasks, fewer photos will be available, but deciphering English characters is also easier than Chinese characters, and we use specifically trained models(with the same structure and different training data). The results are shown in Table~\ref{table-task}.

### 2020-08-17 implementation.tex
newver

In our experiment, we are forced to collect the training dataset on our own instead of using public datasets, as there is no publicly available image dataset built for shoulder-surfing to the best of our knowledge, and because of the uniqueness of our application, i.e. blurriness, targeting characters, working with burst mode snapshots, etc., we cannot find any publicly avaliable substitudes.
%Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

@@

\subsection{Experiment Setting}
\label{sec-experiment-setting}
Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lens and 5 to 7.5 meters for optical lens. Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly time to time, which can simulate a handheld situation. An app runs inside the attacker's phone, taking photos in burst mode repeatedly (no more than 20 photos per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. Screenshots were taken in the victim's phone as ground truth for training and evaluation. An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
\begin{figure}
	\centering
	\includegraphics[width=0.80\linewidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

The data was collected at different times of the day and night, with different illumination and at different positions and angles(tilting no more than 30 degrees). We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels), modifying these environmental parameters every 2,000 images. This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

\subsection{Model Specifications}
It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (less pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features. Thus, the specifications of our model are only for reference and may not work when reproduced on another phone. Also, we may need to repeat the data collection and training phases when switching to another phone model.

Our model accepts any number of images per burst, but it can only process a patch of 9$\times$9 pixels(not necessarily containing whole characters, as it functions at the strokes level) at a time. We expect that characters should be upright(the attacker can simply spin his phone). The model consists of 5 blocks described in the previous section. In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output. the 20$\times$32 feature maps are then merged horizontally with the max-min-average process, and the output is 5$\times$32 channels. Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5$\times$32 channels to form a dataflow of 6$\times$32 channels for each one of the images. These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block. The kernels in each convolutional layer is 3$\times$3. We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks. A single 1$\times$1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer. This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs. As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9$\times$9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

>>>>

In our experiment, we are forced to collect the training dataset on our own instead of using public datasets, as there is no publicly available image dataset built for shoulder-surfing to the best of our knowledge, and because of the uniqueness of our application, i.e. blurriness, targeting characters, working with burst mode snapshots, etc., we cannot find any publicly available substitutes.
%Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

@@

\subsection{Experiment Setting}
\label{sec-experiment-setting}
Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lens and 5 to 7.5 meters for optical lens. Both phones are fixed to stands to keep them completely still, but the lenses with optical zoom will shift slightly from time to time, which can simulate a handheld situation. An app runs inside the attacker's phone, taking photos in burst mode repeatedly(20 images per burst), and another app runs inside the victim's phone, displaying random characters with random fonts and colors. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this character assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. Screenshots were taken in the victim's phone as ground truth for training and evaluation. An illustration of our experimental setting is displayed in Fig.~\ref{illustration_of_system}.
\begin{figure}
	\centering
	\includegraphics[width=0.80\linewidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (distance between phones is shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

The data was collected at different times of the day and night, with different illumination and at different positions and angles(tilting no more than 30 degrees). We collected 800,000 images in this way with a Redmi6A phone (which possesses a camera with 130 million pixels), modifying these environmental parameters every 2,000 images. This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

\subsection{Model Specifications}
It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (fewer pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features. Thus, the specifications of our model are only for reference and may not work when reproduced on another phone. Also, we may need to repeat the data collection and training phases when switching to another phone model.

Our model accepts any number of images per burst, but it can only process a patch of 9$\times$9 pixels(not necessarily containing whole characters, as it functions at the level of strokes) at a time. We expect that characters should be upright(the attacker can simply spin his phone). The model consists of 5 blocks described in the previous section. In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output. the 20$\times$32 feature maps are then merged horizontally with the max-min-average process, and the output is 5$\times$32 channels. Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5$\times$32 channels to form a dataflow of 6$\times$32 channels for each one of the images. These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block. The kernels in each convolutional layer are 3$\times$3. We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks. A single 1$\times$1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer. This model consists of approximately 200,000 parameters and complexity of about 400,000 FLOPs. As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9$\times$9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.
